---
title: "lab04"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab04}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Overview

The `lab04` package provides a lightweight framework for simple linear regression in R. This vignette serves as a guide to understanding and using the main functions provided by the package.

# Installation

To install the `lab04` package, use the following commands:

```{r install-linreg-package, eval=FALSE}
devtools::install_github("yourusername/lab04")
```

# Linear Regression with Linreg

The core function in the Linreg package is linreg S3 class, which initializes a linear regression model with all the caculated values stored as a list. 

This example demonstrates how to create a linreg object and how to use all the exported functions of this linreg S3 class.

## Load required libraries

In this step, we need to load the installed library `lab04`.
The code is showed below.

The required packages will be download and installed automatically.

```{r}
library(lab04)
```

## Create a linreg object
Let's create a simple linear regression model using $iris$ dataset with the formula: $Petal.Length \thicksim Species$.

```{r}
linreg_mod <- linreg(Petal.Length ~ Species, data = iris)
```

## print a Linreg object
```{r}
print(linreg_mod)
```

## plot a Linreg object
```{r}
plot(linreg_mod)
```

## get residuals of regression model
```{r}
resid(linreg_mod)
```

## get fitted values of regression model
```{r}
pred(linreg_mod)
```

## get coef values of regression model
This function use the pre created linreg object as a parameter, and return the coef values of regression model.
```{r}
coef(linreg_mod)
```

## print out the summary of regression model
This function use the pre created linreg object as a parameter, and print out the formula,data name,fitted values,coefficients,Std. Error,p-value,t-value and corresponding visual indicators using p-value.
```{r}
summaery(linreg_mod)
```